---
title: "Applied Survival Analysis Using R"
subtitle: "Chapter 01"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    code_folding: show
    self_contained: true
    highlight: pygments
    keep_md: no
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../docs") })
---

```{r r-setup, include = FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

options(scipen = 999)
options(max.print = "75")
set.seed(12345)

library(pacman)
p_load(asaur)
```

```{r conflicts, include = FALSE}
# tidyverse::tidyverse_conflicts()

conflicted::conflict_scout()
```

```{r knit-setup, include = FALSE}
knitr::opts_chunk$set(cache = FALSE,
                      prompt = FALSE,
                      tidy = FALSE,
                      comment = NA,
                      message = FALSE,
                      warning = FALSE,
                      echo = TRUE)
knitr::opts_knit$set(width = 75)
```

<!-- ----------------------------------------------------- -->

# Data

> Xelox in patients with advanced gastric cancer  

```{r}
data(gastricXelox)

gastricXelox[23:27,]
```

> Pancreatic cancer in patients with locally advanced or metastatic
disease

```{r}
data(pancreatic)

head(pancreatic)
```

> Survival prospects of prostate cancer patients with high-risk disease

```{r}
data(prostateSurvival)

prostateSurvival[88:95,]
```

> Comparison of medical therapies to aid smokers to quit

```{r}
data(pharmacoSmoking)

pharmacoSmoking[1:6, 2:8]
```

> Prediction of survival of hepatocellular carcinoma patients using
biomarkers

```{r}
data(hepatoCellular)

hepatoCellular[c(1, 2, 3, 65, 71), c(2, 3, 16:20, 24, 47)]
```

<!-- ----------------------------------------------------- -->

# Computing Environment

`r mu$session()`